Smart Paper for Examinations

Introduction:
•	Tons of trees were killed for manufacturing paper.
•	Papers we write exams are wasted because of no use after the result.
•	Smart Paper is a tablet where we can write exams, notes, assignments…
•	Textbooks becomes open-source, making it to reach for everyone.
•	Instead of carrying an heavy luggage, we can use this single page.
•	Assignments, Projects can be done easily without much wastage of money,
papers and can be submitted easily on time.

Product Overview:
•	This Smart-Paper is nothing but a Tablet, where we can write anything like
writing on a paper.
•	The OLED display will be made up of Graphene which can be turned into
flexible sheets. So that it experiences as using a paper and reduces eye strain.
•	Graphene can be used as a Power source which is thin and light allows
more power storage capacity and also contains solar charging.
•	No Social Media, No Games and No Entertainment Applications are
installed.
•	Stylus can be used to write on the screen.
•	It has both internal and cloud storage backup.
•	Separate applications (contains a different OS) are installed for different works depending on the situation.

Conducting Examinations:
•	Exams will be smart using this. Instead of papers we can use the same
Tablet to write examination.
•	A Code will be sent to the institution head before 5 minutes of examinations which will help students to access their Booklet Application. After writing the
examination when the student confirms to finish, the file will be securely
encrypted and stored on the respective institutions’ server. If any illegal
activities occur, or any unknown application is installed before the exams,
a notice will be given to respected authorities.
•	Students will get the result immediately after his paper evaluation with a
•	Only-read photocopy. Later we can use as normal book.

Usage of Papers and effects on environment: 
• 93% of paper comes from trees. 
• 50% of the waste of businesses is composed of paper. 
• To print the Sunday edition of the New York Times requires 75,000 trees! 
• It takes an average of 5 litres of water to produce one piece of A4 paper. 
• According to  Indian mirror, Indian Paper Industry accounts about 1.6% of the world’s production of paper and paperboard. 
• Packaging makes up 1/3 or more of our trash. 
• Paper accounts for 25% of landfill waste and 33% of municipal waste. 
• With all the paper we waste each year, we can build a 12 foot high wall of paper from New York to California. 
• Paper pollution is another effect of paper waste and it’s serious problem. It is estimated that by 2020, paper mills will be producing 500,000,000 tons of paper and paperboard each year! 
 
